\huge A Usability Evaluation of Tor Launcher

### 2017-03-03 pets2017-paper/pets2017-paper.tex
Edited up to 7

These were our general observations. Participants who could connect directly or use the recommended bridge had an easy time connecting, but the participants who could not use many of the hardcoded bridges did not know what to do. For a summary of how each participant connected to Tor and what behavioral trends dominated in each environment, see Appendix~\ref{summary}.

\section{Design}
\label{sec:design}

@@

\begin{figure*}
\centering
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-first.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The first screen (F) with reduced, alternative text. We said configuration was required for heavily censorship.}
	\label{fig:new-first}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-proxyYES.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The proxy screen (P). The interface locally detects for a proxy and automatically populates the fields if necessary.}
	\label{fig:new-proxy}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The bridge screen (B). We give users the options to connect with or without a bridge all on one screen, and got rid of the bridge question screen.}
	\label{fig:new-nobridge}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-default.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The bridge menu and additional advice shows up when the corresponding option is chosen. The custom bridge input fields until the custom option is chosen.}
	\label{fig:new-bridge}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-combobox.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{This dropdown menu remains the same (see Figure~\ref{fig:old-bridge-combobox}).}
	\label{fig:new-bridge-combobox}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeHelp.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The bridge help screen (BH) remains the same as well.}
	\label{fig:new-bridge-help}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-summary.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The summary screen (S) summarizes the configuration. This example configuration is connecting directly to Tor.}
	\label{fig:new-summary}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-progress.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The progress bar (Pr) shows the status of each component in the connection as the connection is made.}
	\label{fig:new-progress}
\end{subfigure}
\caption{
A redesigned version of the Tor Browser 5.0.3 Tor Launcher GUI. Screens are in the order that they appear. 
}
\label{fig:new-interface}
\end{figure*}

\subsection{Changes Made} 
We eliminated the bridge and proxy questions from Figure~\ref{fig:old-bridge} and~\ref{fig:old-proxy} and eliminated the proxy screen by simulating auto-detection for proxies. We added a screen to summarize the settings before connecting and added indicators to progress bar that showed what component was unreachable. We switched the proxy and bridge screens so that they are in a topologically sequential order. We clarified that the configure option was for heavily censored environments and gave a secondary bridge recommendation for heavily censored users.

@@

\begin{itemize}
\item {\bfseries User consent}: Using Tor can involve some risk dangerous. While we could help users by automating connection, taking on risk for the user without proper consent is not ethical.

\item{\bfseries Active adversaries}: We could ask the user for their location, risk, or preferences to make decisions. Leveraging user input works well, but third-party versions of Tor Browser that replicate the official version can steal the inputs to profile users.

\item {\bfseries  Passive adversaries}: A sufficiently powerful network adversary can detect that the user is connecting to Tor. We should allow users to leverage local information to reduce their risk.

@@

\item{\bfseries  Financial constraints}: Leveraging harder-to-block meek bridges can help, but these relays cost magnitudes more than other relays and using them more would cost even more money.
\end{itemize}

Other beneficial changes could have been made, if we didn't treat these considerations as constraints.

\section{Quantitative Testing}
\label{sec:quantitative}
To confirm pain points and user behaviors, we logged and quantified user interactions with the interface.

\subsection{Recruitment}
We recruited 65 participants from Craigslist and 59 participants from Xlab participant pool with an ad (Appendix~\ref{quantitative-recruitment}). Xlab encouraged the use of their participant pool, we recruited from Craigslist as well to ensure diversity of participants since its participants were primarily students and staff from UC Berkeley.

>>>>

These were our general observations. Participants who could connect directly (E1) or use the recommended bridge had an easy time connecting (E2), but the participants who could not use many of the hardcoded bridges (E3) did not know what to do. For a summary of how each participant connected to Tor and what behavioral trends dominated in each environment, see Appendix~\ref{summary}.

\section{Interface Redesign}
\label{sec:design}

@@

\begin{figure*}
\centering
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-first.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The first screen (F) with reduced, alternative text. We said configuration was required for heavy censorship.}
	\label{fig:new-first}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-proxyYES.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The proxy screen (P). The interface locally detects a proxy and automatically populates the fields as necessary.}
	\label{fig:new-proxy}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The bridge screen (B). We give users the options to connect with or without a bridge all on one screen, and eliminated the bridge question screen.}
	\label{fig:new-nobridge}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-default.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The bridge menu and additional advice shows up when the corresponding option is chosen. The custom bridge input fields are hidden until the custom option is chosen.}
	\label{fig:new-bridge}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-combobox.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{This dropdown menu remains the same (see Figure~\ref{fig:old-bridge-combobox}).}
	\label{fig:new-bridge-combobox}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeHelp.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The bridge help screen (BH) remains the same as well.}
	\label{fig:new-bridge-help}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-summary.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The summary screen (S) summarizes the configuration. This example configuration is connecting directly to Tor.}
	\label{fig:new-summary}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-progress.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The progress bar (Pr) shows the status of each component in the connection as the connection is made.}
	\label{fig:new-progress}
\end{subfigure}
\caption{
A redesigned version of the Tor Browser 5.0.3 Tor Launcher GUI. Screens are in the order that they appear. 
}
\label{fig:new-interface}
\end{figure*}

\subsection{Changes Made} 
We eliminated the bridge and proxy questions from Figure~\ref{fig:old-bridge} and~\ref{fig:old-proxy} and eliminated the proxy screen by simulating auto-detection for proxies. We added a screen to summarize the settings before connecting and added indicators to the progress bar that showed what component was unreachable. We switched the proxy and bridge screens so that they are in a topologically sequential order. We clarified that configuration options were for heavily censored environments and gave a secondary bridge recommendation for heavily censored users.

@@

\begin{itemize}
\item {\bfseries User consent}: Some oppressive regimes may detect and prosecute Tor usage, and therefore simply using Tor may carry risks. While we could help users by automating configuration settings, this would involve probing network configurations, which may alert authorities to Tor usage. Taking this risk without proper consent is not ethical.

\item{\bfseries Active adversaries}: We could ask the user for their location, risk tolerance, or other preferences to help automatically make decisions. Leveraging user input works well, but third-party versions of Tor Browser that replicate the official version could use these inputs to profile users.

\item {\bfseries Passive adversaries}: A sufficiently powerful network adversary can detect that a user is connecting to Tor. We should allow users to leverage local information to reduce their risk.

@@

\item{\bfseries Financial constraints}: Leveraging harder-to-block ``meek'' bridges, which make use of pay-per-use content delivery networks that are hard to block without imposing collateral damage (e.g., Amazon Web Services), can help, but these relays cost the Tor Project magnitudes more than other relays and using them more would cost even more money.
\end{itemize}

Other beneficial changes could have been made, if we did not consider these constraints.

\section{Quantitative Testing}
\label{sec:quantitative}
To confirm prior pain points and user behaviors, as well as to validate our proposed design improvements, we logged and quantified user interactions as part of a followup experiment.

\subsection{Recruitment}
We recruited 59 participants from the Xlab mailing list, which is a university-wide pool of participants who have opted-in to participating in social science experiments (see Appendix~\ref{quantitative-recruitment} for the recruitment materials). We recruited an additional 65 participants from Craigslist to ensure diversity, since Xlab participants are primarily students and staff from UC Berkeley.
